Local Group Satellite Distributions in the Illustris Simulation

### 2017-10-07 paper/paper.tex
+1 paragraphs

@@

We can quantify the degree at which the observed satellite distributions are 
different from their spherically randomized counterparts.
Figure \ref{fig:lg_distributions} shows the probability distributions
from the \rand\ pairs with an overplot of the LG values.
The upper left panel shows the power law distribution for $\mu$. The
results are not perfectly horizontal because the optimal power value
$\hat{alpha}$ is slightly different from $1$, the uncertainties in
this value are naturally consistent with the unit value expected for
an homogeneous distribution. 
In this case all values are equiprobable.
In the case of the $b/a$ ratio (lower right panel) both the MW and M31
are consistent with the \rand\ distribution.

For all the other cases the Milky Way

>>>>

In Section we list the sources of the observatinal and
simulated data to be used throughout the paper.
Next, in Section we describe the methods we use to quantify and
characterize the satellite distributions.
In section we present our results. 
First we describe the observed satellite distributions and compare
them against the expectation of an spherical randomization of its
satellites. We then compute the expectation from the Illustris Simulation. 
In Section we discuss the implication of our results to finally
summarize in Section.

@@

We can quantify the degree at which the observed satellite distributions are 
different from their spherically randomized counterparts.
Figure \ref{fig:lg_distribution} shows the probability distributions
from the \rand\ pairs with an overplot of the LG values.
The upper left panel shows the power law distribution for $\mu$. The
results are not perfectly horizontal because the optimal power value
$\hat{alpha}$ is slightly different from $1$, the uncertainties in
this value are naturally consistent with the unit value expected for
an homogeneous distribution. 
In this case all values are equiprobable.
In the case of the $b/a$ ratio (lower right panel) both the MW and M31
are consistent with the average values expected from \rand\ distribution.
Remarkably, the plane width and $c/a$ ratio for the MW are significantly 
different from the \rand\ expected values, while the M31 values are
sistematically within the expectations.

The comparison of the observed satellite distribution against its onw
version, but spherically randomized, tells us that the MW satellite
planar structure is remarkably different from a random distribution,
while for the M31 distribution there isn't a significant difference
from the random expectation.

\subsection{Satellite distributions in the Illustris Simulation}

In the previous section we saw how the MW cannot be concealed with its
randomized satellite distribution, while M31 is fully consistent with
it. 
We now quantify whether the MW and M31 are consistent with the
expectations from the Illustris Simulation.
We show here the results from the \rank\ sample. 
The results from the \boot\ sample ara avaialble in the appendix.
